Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-04-27 fib2.tex
yes i am finally thinking about this again

\newcommand{\cggb}[1]{\textcolor{blue}{#1}}
\newcommand{\sdb}[1]{\textcolor{red}{#1}}
\newcommand{\stf}[1]{\textcolor{green}{#1}}

@@

@@

We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
microscopic details of the system. This is consistent with the principles of topologically 
ordered systems and anyonic physics, where the key universal features describing the 
anyon model correspond to large length-scale physics, while the microscopic physics plays 
a less important (and non-universal) role. As such, we model the system simply as a 
periodic $L\times L$ square lattice $\Lambda$ of sites with upon which sets of anyons can 
reside. Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
locally on edges of $\Lambda$. For more details of an analogous model, see~\cite{Brell2013}.

@@

In order to perform a logical error on our code, a noise process must have support on a 
ribbon running around a homologically nontrivial loop of the lattice. These correspond to 
processes in which anyonic charge is transported around the non-trivial loop before 
annihilating to vacuum.

@@

Our concrete simulation proceeds by associating a \emph{tile} with each site of the 
$L\times L$ periodic square lattice. In order to keep track of the observables of the system 
we maintain a set of disjoint curves, representing the history of anyons on the lattice (these 
curves can also be thought of as a top-down view of the fusion tree). 
\stf{this next sentence is currently incorrect.} \cggb{Why?}
The ends of curves 
correspond to leaves of the fusion tree, or anyons. In general, the curves wind around the two 
dimensional tiles in a haphazard way determined by the progress of the simulation. This 
allows a dynamically generated basis for the fusion space that easily allows for tensor 
decomposition into factors corresponding to disjoint clusters. For comparison, previous work 
used a single fixed basis for the fusion space (determined by row-major ordering of 
sites)~\cite{Brell2013}.

@@

\begin{figure}[th!]
\begin{center}
	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
\caption{Decoder failure as a function of simulation time for various lattice sizes, showing 
threshold behavior around at $t_{\mathrm{sim}}\simeq 0.125$.}
\label{f:threshold}
\end{center}
\end{figure}

@@

\cggb{Comment on the effect of declaring failure on some simulations on this plot. Would 
we expect it to change if we simulated every event completely? If so, how?}

@@

\stf{Is there a possibility of using MPS like Rob Pfeiffer to improve the simulations or 
include interactions?}

>>>>

\newcommand{\cggb}[1]{\textcolor{blue}{#1}}
\newcommand{\dude}[1]{\textcolor{red}{#1}}
\newcommand{\stf}[1]{\textcolor{green}{#1}}

@@

\dude{we should stress the distinction between
simulation the fib dynamics and the simulation of
the decoder (which is poly by design).. this is something
that doherty completely missed at first.. the decoder is
classical and it does not care what anyon system it is
looking at.}

@@

We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
microscopic details of the system. 
\dude{Another way of saying this is that we are doing a tqft simulation.}
This is consistent with the principles of topologically 
ordered systems and anyonic physics, where the key universal features describing the 
anyon model correspond to large length-scale physics, while the microscopic physics plays 
a less important (and non-universal) role. As such, we model the system simply as a 
periodic $L\times L$ square lattice $\Lambda$ of sites with upon which sets of anyons can 
reside. Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
locally on edges of $\Lambda$. For more details of an analogous model, see~\cite{Brell2013}.

\dude{I really need to see something about observables vs. states. Even if
we dont mention tqft.}

@@

In order to perform a logical error on our code, a noise process must have support on a 
ribbon running around a homologically nontrivial loop of the lattice. These correspond to 
processes in which anyonic charge is transported around the non-trivial loop before 
annihilating to vacuum \dude{or not}.

@@

Our concrete simulation proceeds by associating a \emph{tile} with each site of the 
$L\times L$ periodic square lattice.
In order to keep track of the observables of the system 
we maintain a set of disjoint curves, representing the history of anyons on the lattice.
These curves can also be thought of as a top-down view of the fusion tree:
the anyons on the leaves of the fusion tree are here displayed as points along each curve.
%The ends of curves correspond to leaves of the fusion tree, or anyons. 
In general, the curves wind around the two 
dimensional tiles in a haphazard way determined by the progress of the simulation.
This allows a dynamically generated basis for the fusion space that easily allows for tensor 
decomposition into factors corresponding to disjoint clusters.
For comparison, previous work 
used a single fixed basis for the fusion space (determined by row-major ordering of 
sites)~\cite{Brell2013}.

@@

\begin{figure}[th!]
\begin{center}
	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
\caption{Decoder failure as a function of simulation time for various lattice sizes, showing 
threshold behavior at around $t_{\mathrm{sim}}\simeq 0.125$.}
\label{f:threshold}
\end{center}
\end{figure}

@@

\cggb{Comment on the effect of declaring failure on some simulations on this plot. Would 
we expect it to change if we simulated every event completely? If so, how?}
\dude{you spend alot of effort arguing above that we can
neglect these occurances, but i am wondering if we need to be
this strenuous: i did many calculations of global braids/fusions
and they all do a non-unitary on the logical space.. i could not
see how to braid around the torus in *any* trivial way *at all*.
This falls short of a proof, but i'm fairly convinced our sim is
in fact 100 percent correct.}

@@

\stf{Is there a possibility of using MPS like Rob Pfeiffer to improve the simulations or 
include interactions?}
\dude{Our simulation is effectively doing a contraction of a 2d peps-like network. So
yeah, maybe there are connections.}
